---
title: "MCC Preference Kids"
author: "Manuel Bohn"
date: "23 7 2018"
output: html_document
---

```{r setup, include= FALSE}
knitr::opts_chunk$set(echo = FALSE)
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)


## importing data

# d_ipad <- read_csv(file="kids_pref.data.csv")
# 
# d_hand_code <- read.csv(file="kids_pref_handcoding.data.csv", sep = ";")%>%
#   mutate(age_num = as.numeric(as.character(age_num)))
# 
# d <- bind_rows(d_ipad,d_hand_code)%>%
#   mutate(trial_type = ifelse(trial == "train", "train", "test"))%>%
#   filter(subid != "200718_8_pref")
# 
# 
# # check if someone needs to be excluded because wrong in training
# # no one
# d %>%
#   filter(trial_type == "train") %>%
#   group_by(subid)%>%
#   summarise(correct = mean(correct)) %>%
#   filter(correct == 0)

d <- read_csv(file="../data/kids_pref_data.csv")


```

# Subjects

There was one additional 4yo in the data set, whom I excluded to get the pre-registered sample size of 45 total. For the modeling we might want to include her as that gives us a tiny bit more precision.

## Overall

All training trials were answered correctly, suggesting that children generally understood the procedure. Sex is not included in the data set but the sex ration is fairly balances across age bins (47 to 60% girls).

```{r sanity checks, echo = FALSE,warning = FALSE, message = FALSE}


## sanity checks
d %>%
  group_by(trial_type) %>%
  summarise(n = length(unique(subid)), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 2)


```

## By age bin

Just to check if we got the planned sample size of 15 per bin.

```{r kids per age group,echo = FALSE}

d %>%
  group_by(age)%>%
  summarise(n = length(unique(subid)),
            age_num = mean(age_num))%>%
  knitr::kable(digits = 2)
```

# Plots

## Plot across age bins

Medium overall effect of speaker change.

```{r plot across age}
p3 <- d %>%
  filter(trial_type == "test") %>%
  group_by(change, subid) %>%
  summarise(correct = mean(correct)) 

p4 <- p3 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p3, aes(x = change, y = correct, col = change, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p4, aes(x = change, y = mean, col = change, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Speaker Change",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

## Plot by age bin

The following two plots suggest some sort of linear developmental trajectory.

```{r plot by age}
p1 <- d %>%
  filter(trial_type == "test") %>%
  group_by(change,age, subid) %>%
  summarise(correct = mean(correct)) 

p2 <- p1 %>%
  multi_boot_standard(col = "correct")


ggplot() +
  geom_jitter(data = p1, aes(x = change, y = correct, col = change, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = change, y = mean, col = change, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_wrap(~age)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Speaker Change",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

## Plot with age as continuous variable

```{r plot by numerical age}
p5 <- d %>%
  filter(trial_type == "test") %>%
  group_by(change,age_num, subid) %>%
  summarise(correct = mean(correct)) 

ggplot(data = p5, aes(x = age_num, y = correct, col = change)) +
  geom_smooth(method = "loess", se = T)+
  geom_jitter( alpha = .5, height = 0.04)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Speaker Change",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

# Inference

## T-tests against chance across age bins
```{r}
## t tests against chance
d %>%
  filter(trial_type == "test") %>%
  group_by(change, subid) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(change) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
  select(change,df,t_value,p_value) %>%
  knitr::kable(digits = 3)


```

## T-tests against chance per age bin
```{r}
## t tests against chance
d %>%
  filter(trial_type == "test") %>%
  group_by(age,change, subid) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(age,change) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
  select(age,change,df,t_value,p_value) %>%
  knitr::kable(digits = 3)
 
```

## GLMM

With age as continuous variable. We pre-registered the model with an interaction between age and change as a random slope for subject: `(change * age| subid)`. However, including age here seems unnecessary since each subject has only one age. I therefore took the interaction out in the model below.

Results mirror what we see in the plots above: increasing effect of speaker change across development.

```{r}
## model
library(lme4)

lm_data <- d%>%
  filter(trial_type == "test")%>%
  mutate(choiceAgent = ifelse( change == F, agent, altAgent),
         age_num = scale(age_num, center = TRUE, scale = TRUE))

# maximal converging model
lm <- glmer(correct ~ age_num * change + (change | subid) + (age_num * change | choiceAgent), 
              data = lm_data, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(lm)

```

# Additional plots

To check for trial and item effects.

## Conditions by trial
```{r plot trials}
ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(change, trial, subid) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = trial, y = mean, col = change)) +
  geom_line(aes(group= change)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  theme_few() + 
  scale_colour_solarized()
```

## By agent
```{r plot agents}
ms <- d %>%
  filter(trial_type == "test") %>%
  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
  group_by(change, choiceAgent, subid) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = choiceAgent, y = mean, col = change)) +
  geom_line(aes(group= change)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  theme_few() + 
  scale_colour_solarized()
```





