---
title: "MCC Models"
author: "Manuel Bohn"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(knitr)
library(ggthemes)
library(langcog)
library(rwebppl)
library(coda)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}

```

# Model code

## Model utensils

```{r rsaUtils, include = FALSE}
rsaUtils <- '
var all_objects = [
{ shape: "triangle", id:1, location: 1},  
{ shape: "triangle", id:2, location: 2},
{ shape: "circle", id:1, location: 2}
]

var prior_objects = [
{ shape: "triangle", id:1, location: 1},  
{ shape: "circle", id:1, location: 2}
]

var labels = ["dax","wug"]

var lexicon1 = function(utterance, obj){
utterance.label == "dax" ? obj.shape == "triangle" :
utterance.label == "wug" ? obj.shape == "circle" : 
true
}

var lexicon2 = function(utterance, obj){
utterance.label == "dax" ? obj.shape == "circle" :
utterance.label == "wug" ? obj.shape == "triangle" : 
true
}

var lexiconObjects = {
"dax = triangle": {
triangle: "dax", circle: "wug"
},
"dax = circle": {
triangle: "wug", circle: "dax"
},
}

var lexiconObject = {
"dax = triangle": lexicon1,
"dax = circle" : lexicon2
}

var point = function(utterance, obj){
return obj.location == utterance.point
}


var utterancePrior = function(obj, lexiconName){
var locationsWithShape = _.map(_.filter(all_objects, {shape: obj.shape}), "location")
var point = uniformDraw(locationsWithShape)
var label = lexiconObjects[lexiconName][obj.shape]
return {label: label, point: point}
}

var LexiconPrior = Categorical({vs: ["dax = triangle","dax = circle" ], ps: [1, 1]})

var speakerOptimality = 2.25;

var addNoise = function(dist, noiseParam){
   Infer({model: function(){ 
      return flip(noiseParam) ? uniformDraw([0, 1]) : sample(dist)
    }
   })
}

var foreach = function(fn, lst) {
    var foreach_ = function(i) {
        if (i < lst.length) {
            fn(lst[i]);
            foreach_(i + 1);
        }
    };
    foreach_(0);
};

var logistic = function(x) {1 / (1 + Math.exp(-x))}

var levels = function(df, label){
  return _.uniq(_.map(df, label));
}

'
```

# Adults

## RSA model code 

```{r rsaModel}
rsaModel <- '
var pragmaticListener = function(utterance, priorProbs){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior);
var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
var S1 = speaker(obj, lexiconName, priorProbs);
observe(S1, utterance)
return obj.shape == "circle" ? 1 : 0
}})
}

var speaker = function(obj, lexiconName, priorProbs){
Infer({method: "enumerate", model: function(){
var utterance = utterancePrior(obj, lexiconName);
var L0 = literalListener(utterance, priorProbs);
 factor(speakerOptimality * L0.score(obj.shape))
return utterance
}})
}

var literalListener = function(utterance, priorProbs){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior); 
var lexicon = lexiconObject[lexiconName];
var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
if ("label" in utterance) {
 var truthValue = lexicon(utterance, obj);
 condition(truthValue)
}
if (utterance.point) {
 var truthValuePoint = point(utterance, obj);
 condition(truthValuePoint)
}
return obj.shape 
}})
}
'
```

## Experiment 3

### Model parameters and data

```{r ex3 data}
# load data from experiment 3
adult_ex3_data <-read_csv(file="../../stats/data/adult_ex3.csv") 
```

```{r}
# load data from prior manipulation experiments to set priors
adult_ex2_novelty_data <- read_csv(file="../../stats/data/adult_ex2_novelty.csv")
adult_ex2_preference_data <- read_csv(file="../../stats/data/adult_ex2_preference.csv")
```

```{r model setup ex 4, include = FALSE}

# create datafiles with model parameters
predPriorEx3 <- data.frame(
  common_ground_manipulation = c("preference","preference","preference","preference","novelty","novelty","novelty","novelty"),
  speaker = c("same_speaker","same_speaker","different_speaker","different_speaker","same_speaker","same_speaker","different_speaker","different_speaker"),
  alignment = c("congruent","incongruent","congruent","incongruent","congruent","incongruent","congruent","incongruent"))

prior_pref_same <- adult_ex2_preference_data %>%
  filter(condition == "same_speaker")%>%
  summarise(prior = mean(correct))

prior_pref_diff <- adult_ex2_preference_data %>%
  filter(condition == "different_speaker")%>%
  summarise(prior = mean(correct))

prior_novel_same <- adult_ex2_novelty_data %>%
  filter(condition == "same_speaker")%>%
  summarise(prior = mean(correct))

prior_novel_diff <- adult_ex2_novelty_data %>%
  filter(condition == "different_speaker")%>%
  summarise(prior = mean(correct))

predPriorEx3$prior = list(
    c(1-prior_pref_same$prior,1-prior_pref_same$prior,prior_pref_same$prior), 
    c(prior_pref_same$prior,prior_pref_same$prior,1-prior_pref_same$prior), 
    c(1-prior_pref_diff$prior,1-prior_pref_diff$prior,prior_pref_diff$prior), 
    c(prior_pref_diff$prior,prior_pref_diff$prior,1-prior_pref_diff$prior),
    c(1-prior_novel_same$prior,1-prior_novel_same$prior,prior_novel_same$prior), 
    c(prior_novel_same$prior,prior_novel_same$prior,1-prior_novel_same$prior), 
    c(1-prior_novel_diff$prior,1-prior_novel_diff$prior,prior_novel_diff$prior), 
    c(prior_novel_diff$prior,prior_novel_diff$prior,1-prior_novel_diff$prior))

# data frame to keep track of unique conditions
allConditionsEx3 <- predPriorEx3 %>%
  select(-prior)

```

### Model predictions

##### Pragmatic model

```{r model rsa noise ex3, include = FALSE}
predictions.rsa.ex3 <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.predPrior

var model = function(){
   var noise = uniformDrift({a: 0, b:1, width: 0.1})

  var conditionOutput = map(function(conditionInfo){

  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})

   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})

   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].prior)
   var noisyModelPredictions = addNoise(modelPredictions, noise)

   map(function(d){ 
      observe(noisyModelPredictions, d.correct_inf)
    }, conditionSpecificData)


  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]

}, allConditions)

  return extend(_.fromPairs(conditionOutput), {noise: noise})

}
'
```

```{r predictions pragmatic model ex 3, include = FALSE}

# ex3_pragm_model <- webppl(
#   program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex3, sep='\n'),
#   data = list(allData = adult_ex3_data, allConditions = allConditionsEx3, predPrior = predPriorEx3),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
# ) %>%
#   saveRDS("../../stats/saves/ex3_pragm_model.rds")

ex3_pragm_model <- readRDS("../../stats/saves/ex3_pragm_model.rds")

# model predictions
ex3_pragm_model_pred <- ex3_pragm_model %>%
  filter(!(Parameter %in% c("noise")))  %>%
  separate(Parameter, into = c("common_ground_manipulation","speaker", "alignment"), sep="/")%>%
  mutate(model="pragmatic")


## noise parameter
ex3_pragm_model_noise <- ex3_pragm_model %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

```

##### Prior only model

```{r model prior only ex3 , include = FALSE}
predictions.prior.only.ex3 <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.predPrior

var model = function(){
   var noise = uniformDrift({a: 0, b:1, width: 0.1})

  var conditionOutput = map(function(conditionInfo){

  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})

   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})

  var modelPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].prior}));
      return obj.shape == "circle" ? 1 : 0
  }})

   var noisyModelPredictions = addNoise(modelPredictions, noise)

   map(function(d){ 
      observe(noisyModelPredictions, d.correct_inf)
    }, conditionSpecificData)


  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]

}, allConditions)

return extend(_.fromPairs(conditionOutput), {noise: noise})

}
'
```

```{r predictions prior only model ex3, include = FALSE}

# ex3_prior_only_model <- webppl(
#   program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex3, sep='\n'),
#   data = list(allData = adult_ex3_data, allConditions = allConditionsEx3, predPrior = predPriorEx3),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
# ) %>%
#   saveRDS("../../stats/saves/ex3_prior_only_model.rds")

ex3_prior_only_model <- readRDS("../../stats/saves/ex3_prior_only_model.rds")

# model predictions
ex3_prior_only_model_pred <- ex3_prior_only_model %>%
  filter(!(Parameter %in% c("noise")))  %>%
  separate(Parameter, into = c("common_ground_manipulation", "speaker", "alignment"), sep="/")%>%
  mutate(model="prior_only")


## noise parameter
ex3_prior_only_model_noise <- ex3_prior_only_model %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

```

##### Flat prior model

```{r model flat prior ex3, include = FALSE}
predictions.flat.prior.ex3 <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.predPrior

var model = function(){
   var noise = uniformDrift({a: 0, b:1, width: 0.1})

  var conditionOutput = map(function(conditionInfo){

  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})

   var conditionSpecificPriors = [.5, .5, .5] 

   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors)
   var noisyModelPredictions = addNoise(modelPredictions, noise)

   map(function(d){ 
      observe(noisyModelPredictions, d.correct_inf)
    }, conditionSpecificData)


  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]

}, allConditions)

  return extend(_.fromPairs(conditionOutput), {noise: noise})

}
'
```

```{r predictions prior only model ex3, include = FALSE}

# ex3_flat_prior_model <- webppl(
#   program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex3, sep='\n'),
#   data = list(allData = adult_ex3_data, allConditions = allConditionsEx3, predPrior = predPriorEx3),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
# ) %>%
#   saveRDS("../../stats/saves/ex3_flat_prior_model.rds")

ex3_flat_prior_model <- readRDS("../../stats/saves/ex3_flat_prior_model.rds")

# model predictions
ex3_flat_prior_model_pred <- ex3_flat_prior_model %>%
  filter(!(Parameter %in% c("noise")))  %>%
  separate(Parameter, into = c("common_ground_manipulation", "speaker", "alignment"), sep="/")%>%
  mutate(model="flat_prior")


## noise parameter
ex3_flat_prior_model_noise <- ex3_flat_prior_model %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

```

```{r}
# combine model predictions with data 

# summarize data 
adult_ex3_data_summary <- adult_ex3_data %>%
  mutate(model = "data") %>%
  group_by(model,common_ground_manipulation,speaker,alignment)%>%
  summarize(k = sum(correct_inf), n = n())%>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         ci_lower  = qbeta(.025, a, b),
         ci_upper = qbeta(.975, a, b),
         mean = (a-1)/(a+b-2))%>%
  select(-a,-b,-n,-k)

# summarize model predictions
ex_3_model_pred <- bind_rows(
  ex3_pragm_model_pred,
  ex3_prior_only_model_pred,
  ex3_flat_prior_model_pred
)%>%
  group_by(model,common_ground_manipulation,speaker,alignment) %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value), 
            ci_upper = hdi_upper(value))

# combine model predictions and data

ex_3_pred <- bind_rows(
  ex_3_model_pred,
  adult_ex3_data_summary
)

#saveRDS(ex_3_pred, "../../stats/saves/ex3_model_predictions.rds")

```

##### Plot model predictions and data

```{r plot ex3 model predictions and data}
ggplot(data = ex_3_pred, aes(x = alignment, y = mean, col = model)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), size = .4,  position = position_dodge(width = .5), pch = 5)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Choosing More Informative")+
  facet_grid (~ common_ground_manipulation + speaker) +
  theme_few() + 
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_color_manual(name="Model",
                     breaks=c("data","pragmatic","flat_prior","prior_only"),
                     values= c("black","#859900","#6c71c4","#b58900"))+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
```

##### Correlation plot model predictions and data

```{r plot }

ex_3_cor_plot <- ex_3_pred %>%
  ungroup()%>%
  filter(model != "data") %>%
  mutate(data_mean = rep(ex_3_pred%>%filter(model == "data")%>%pull(mean),3),
         data_ci_lower = rep(ex_3_pred%>%filter(model == "data")%>%pull(ci_lower),3),
         data_ci_upper = rep(ex_3_pred%>%filter(model == "data")%>%pull(ci_upper),3))
  


ggplot(data = ex_3_cor_plot,aes(x = mean, y = data_mean, col = "#BB5566")) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
  geom_point(size = 2)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .7)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  guides(col = F)+
  facet_grid ( ~ model) +
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = data_mean), inherit.aes = F, size = 3)+
  theme_few()

```

### Model comparison

```{r model likelihood rsa ex3, include = FALSE}
loglike.rsa.ex3 <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.predPrior

var model = function(){
   var noise = uniformDrift({a: 0, b:1, width: 0.1})

  var conditionOutput = map(function(conditionInfo){

  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})

   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})

   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].prior)
   
    var noisyModelPredictions = addNoise(modelPredictions, noise)

    var loglike = Binomial({
        p: Math.exp(noisyModelPredictions.score(1)), 
        n: conditionSpecificData.length}).score(
      sum(_.map(conditionSpecificData, "correct_inf"))
    )

  return  loglike

}, allConditions)

 return sum(conditionOutput)

}
'
```

```{r model likelihood prior only ex3 , include = FALSE}
loglike.prior.only.ex3 <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.predPrior

var model = function(){
   var noise = uniformDrift({a: 0, b:1, width: 0.1})

  var conditionOutput = map(function(conditionInfo){

  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})

   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})

  var modelPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].prior}));
      return obj.shape == "circle" ? 1 : 0
  }})

   var noisyModelPredictions = addNoise(modelPredictions, noise)

    var loglike = Binomial({
        p: Math.exp(noisyModelPredictions.score(1)), 
        n: conditionSpecificData.length}).score(
      sum(_.map(conditionSpecificData, "correct_inf"))
    )

  return  loglike

}, allConditions)

 return sum(conditionOutput)

}
'
```

```{r model likelihood flat prior ex3, include = FALSE}
loglike.flat.prior.ex3 <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.predPrior

var model = function(){
   var noise = uniformDrift({a: 0, b:1, width: 0.1})

  var conditionOutput = map(function(conditionInfo){

  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})

   var conditionSpecificPriors = [.5, .5, .5] 

   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors)
   var noisyModelPredictions = addNoise(modelPredictions, noise)

    var loglike = Binomial({
        p: Math.exp(noisyModelPredictions.score(1)), 
        n: conditionSpecificData.length}).score(
      sum(_.map(conditionSpecificData, "correct_inf"))
    )

  return  loglike

}, allConditions)

 return sum(conditionOutput)

}
'
```

```{r ex3 model comparison}
# ex3_pragm_model_loglike <- webppl(
#   program_code = paste(rsaUtils, rsaModel, loglike.rsa.ex3, sep='\n'),
#   data = list(allData = adult_ex3_data, allConditions = allConditionsEx3, predPrior = predPriorEx3),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4, 
#   cores = 4,
#   inference_opts = list(method = "forward", samples = 5000)
# ) %>%
#   saveRDS("../../stats/saves/ex3_pragm_model_loglike.rds")

ex3_pragm_model_loglike <- readRDS("../../stats/saves/ex3_pragm_model_loglike.rds")%>%
  mutate(model = "pragmatic")%>%
  group_by(model)%>%
  summarize(logP = logSumExp(value))

# ex3_prior_only_model_loglike <- webppl(
#   program_code = paste(rsaUtils, rsaModel, loglike.prior.only.ex3, sep='\n'),
#   data = list(allData = adult_ex3_data, allConditions = allConditionsEx3, predPrior = predPriorEx3),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4, 
#   cores = 4,
#   inference_opts = list(method = "forward", samples = 5000)
# )%>%
#   saveRDS("../../stats/saves/ex3_prior_only_model_loglike.rds")

ex3_prior_only_model_loglike <- readRDS("../../stats/saves/ex3_prior_only_model_loglike.rds")%>%
  mutate(model = "prior_only")%>%
  group_by(model)%>%
  summarize(logP = logSumExp(value))


# ex3_flat_prior_model_loglike <- webppl(
#   program_code = paste(rsaUtils, rsaModel, loglike.flat.prior.ex3, sep='\n'),
#   data = list(allData = adult_ex3_data, allConditions = allConditionsEx3, predPrior = predPriorEx3),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4, 
#   cores = 4,
#   inference_opts = list(method = "forward", samples = 5000)
# )%>%
#   saveRDS("../../stats/saves/ex3_flat_prior_model_loglike.rds")

ex3_flat_prior_model_loglike <- readRDS("../../stats/saves/ex3_flat_prior_model_loglike.rds")%>%
  mutate(model = "flat_prior")%>%
  group_by(model)%>%
  summarize(logP = logSumExp(value))

ex3_model_comparison <- bind_rows(
  ex3_pragm_model_loglike,
  ex3_prior_only_model_loglike,
  ex3_flat_prior_model_loglike
)%>%
  mutate(model = reorder(model,logP))

#saveRDS(ex3_model_comparison, "../../stats/saves/ex3_model_comparison.rds")

```
##### Plot for likelihoods

```{r}
ggplot(ex3_model_comparison, aes(x = model, y = logP, col = model))+
  geom_segment( aes(x=model, xend=model, y=0, yend=logP), col = "black", size = 1)+
  geom_point(size = 7)+
  theme_few()+ 
  xlab("Model")+
  ylab("Log-likelihood")+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(col = F)+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#859900","#b58900","#6c71c4"))
```


##### Bayes factors

```{r}
ex3_bf <- data.frame(
  comparison = c("pragmatic vs. prior_only","pragmatic vs. flat_prior", "flat_rior vs. prior_only"),
  bayes_factor = c(
    exp(ex3_model_comparison$logP[ex3_model_comparison$model== "pragmatic"] - ex3_model_comparison$logP[ex3_model_comparison$model== "prior_only"]),
    exp(ex3_model_comparison$logP[ex3_model_comparison$model== "pragmatic"] - ex3_model_comparison$logP[ex3_model_comparison$model== "flat_prior"]),
    exp(ex3_model_comparison$logP[ex3_model_comparison$model== "prior_only"] - ex3_model_comparison$logP[ex3_model_comparison$model== "flat_prior"]))
)

ex3_bf%>%
  kable(digits = 2)
```

## Experiment 4

### Model parameters and data
```{r ex4 data}
# load data  from experiment 4 
adult_ex4_data <-read_csv(file="../../stats/data/adult_ex4.csv") 
```

```{r}
# load data from prior strength manipulation experiments to set priors
adult_ex4_prior_data <-read_csv(file="../../stats/data/adult_ex4_prior.csv") 
```

```{r model setup ex 4, include = FALSE}

# create datafiles with model parameters

strongPrior <- data.frame(
  common_ground_manipulation = c("preference","preference","preference","preference","novelty","novelty","novelty","novelty"),
  speaker = c("same_speaker","same_speaker","different_speaker","different_speaker","same_speaker","same_speaker","different_speaker","different_speaker"),
  alignment = c("congruent","incongruent","congruent","incongruent","congruent","incongruent","congruent","incongruent"),
  prior_manipulation = rep("strong",8))

strong_prior_pref_same <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "preference",
         prior_manipulation == "strong",
         speaker == "same_speaker")%>%
  summarise(prior = mean(correct))

strong_prior_pref_diff <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "preference",
         prior_manipulation == "strong",
         speaker == "different_speaker")%>%
  summarise(prior = mean(correct))

strong_prior_novel_same <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "novelty",
         prior_manipulation == "strong",
         speaker == "same_speaker")%>%
  summarise(prior = mean(correct))

strong_prior_novel_diff <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "novelty",
         prior_manipulation == "strong",
         speaker == "different_speaker")%>%
  summarise(prior = mean(correct))

strongPrior$prior = list(
    c(1-strong_prior_pref_same$prior,1-strong_prior_pref_same$prior,strong_prior_pref_same$prior), 
    c(strong_prior_pref_same$prior,strong_prior_pref_same$prior,1-strong_prior_pref_same$prior), 
    c(1-strong_prior_pref_diff$prior,1-strong_prior_pref_diff$prior,strong_prior_pref_diff$prior), 
    c(strong_prior_pref_diff$prior,strong_prior_pref_diff$prior,1-strong_prior_pref_diff$prior),
    c(1-strong_prior_novel_same$prior,1-strong_prior_novel_same$prior,strong_prior_novel_same$prior), 
    c(strong_prior_novel_same$prior,strong_prior_novel_same$prior,1-strong_prior_novel_same$prior), 
    c(1-strong_prior_novel_diff$prior,1-strong_prior_novel_diff$prior,strong_prior_novel_diff$prior), 
    c(strong_prior_novel_diff$prior,strong_prior_novel_diff$prior,1-strong_prior_novel_diff$prior))

mediumPrior <- data.frame(
  common_ground_manipulation = c("preference","preference","preference","preference","novelty","novelty","novelty","novelty"),
  speaker = c("same_speaker","same_speaker","different_speaker","different_speaker","same_speaker","same_speaker","different_speaker","different_speaker"),
  alignment = c("congruent","incongruent","congruent","incongruent","congruent","incongruent","congruent","incongruent"),
  prior_manipulation = rep("medium",8))

medium_prior_pref_same <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "preference",
         prior_manipulation == "medium",
         speaker == "same_speaker")%>%
  summarise(prior = mean(correct))

medium_prior_pref_diff <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "preference",
         prior_manipulation == "medium",
         speaker == "different_speaker")%>%
  summarise(prior = mean(correct))

medium_prior_novel_same <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "novelty",
         prior_manipulation == "medium",
         speaker == "same_speaker")%>%
  summarise(prior = mean(correct))

medium_prior_novel_diff <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "novelty",
         prior_manipulation == "medium",
         speaker == "different_speaker")%>%
  summarise(prior = mean(correct))

mediumPrior$prior = list(
    c(1-medium_prior_pref_same$prior,1-medium_prior_pref_same$prior,medium_prior_pref_same$prior), 
    c(medium_prior_pref_same$prior,medium_prior_pref_same$prior,1-medium_prior_pref_same$prior), 
    c(1-medium_prior_pref_diff$prior,1-medium_prior_pref_diff$prior,medium_prior_pref_diff$prior), 
    c(medium_prior_pref_diff$prior,medium_prior_pref_diff$prior,1-medium_prior_pref_diff$prior),
    c(1-medium_prior_novel_same$prior,1-medium_prior_novel_same$prior,medium_prior_novel_same$prior), 
    c(medium_prior_novel_same$prior,medium_prior_novel_same$prior,1-medium_prior_novel_same$prior), 
    c(1-medium_prior_novel_diff$prior,1-medium_prior_novel_diff$prior,medium_prior_novel_diff$prior), 
    c(medium_prior_novel_diff$prior,medium_prior_novel_diff$prior,1-medium_prior_novel_diff$prior))


weakPrior <- data.frame(
  common_ground_manipulation = c("novelty","novelty","novelty","novelty"),
  speaker = c("same_speaker","same_speaker","different_speaker","different_speaker"),
  alignment = c("congruent","incongruent","congruent","incongruent"),
  prior_manipulation = rep("weak",4))

weak_prior_novel_same <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "novelty",
         prior_manipulation == "weak",
         speaker == "same_speaker")%>%
  summarise(prior = mean(correct))

weak_prior_novel_diff <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "novelty",
         prior_manipulation == "weak",
         speaker == "different_speaker")%>%
  summarise(prior = mean(correct))

weakPrior$prior = list(
    c(1-weak_prior_novel_same$prior,1-weak_prior_novel_same$prior,weak_prior_novel_same$prior), 
    c(weak_prior_novel_same$prior,weak_prior_novel_same$prior,1-weak_prior_novel_same$prior), 
    c(1-weak_prior_novel_diff$prior,1-weak_prior_novel_diff$prior,weak_prior_novel_diff$prior), 
    c(weak_prior_novel_diff$prior,weak_prior_novel_diff$prior,1-weak_prior_novel_diff$prior))

# combining all priors into one data frame
predPriorEx4 = rbind(strongPrior,mediumPrior,weakPrior)

# data frame to keep track of unique conditions
allConditionsEx4 <- predPriorEx4 %>%
  select(-prior)

```

### Model predictions

##### Pragmatic model

```{r model rsa noise ex4, include = FALSE}
predictions.rsa.ex4 <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.predPrior
var noise = dataFromR.noise[0]

var conditionOutput = map(function(conditionInfo){

    var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})

    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].prior)
   
    var noisyModelPredictions = addNoise(modelPredictions, noise)

    return  extend([conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment+ "/" + conditionInfo.prior_manipulation, Math.exp(noisyModelPredictions.score(1))])

  }, allConditions)

   conditionOutput


'
```

```{r predictions pragmatic model, include = FALSE}

ex4_pragm_model <- webppl(
  program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex4, sep='\n'),
  data = list(allData = adult_ex4_data, allConditions = allConditionsEx4, predPrior = predPriorEx4, noise = ex3_pragm_model_noise$mean),
  data_var = "dataFromR"
)

# model predictions
ex4_pragm_model_pred <- ex4_pragm_model %>%
  separate(`0`, into = c("common_ground_manipulation", "speaker", "alignment", "prior_manipulation"), sep="/")%>%
  mutate(value = `1`,
         model="pragmatic",
         prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))%>%
  select(-`1`)

```

##### Prior only model 

```{r model prior only ex4 , include = FALSE}
predictions.prior.only.ex4 <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.predPrior
var noise = dataFromR.noise[0]

var conditionOutput = map(function(conditionInfo){

   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})

  var modelPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].prior}));
      return obj.shape == "circle" ? 1 : 0
  }})

   var noisyModelPredictions = addNoise(modelPredictions, noise)

  return  extend([conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment+ "/" + conditionInfo.prior_manipulation, Math.exp(noisyModelPredictions.score(1))])


}, allConditions)

conditionOutput

'
```


```{r predictions prior only model ex 4, include = FALSE}

ex4_prior_only_model <- webppl(
  program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex4, sep='\n'),
  data = list(allData = adult_ex4_data, allConditions = allConditions, predPrior = predPrior, noise = ex3_prior_only_model_noise$mean),
  data_var = "dataFromR"
) 

# model predictions
ex4_prior_only_model_pred <- ex4_prior_only_model %>%
  separate(`0`, into = c("common_ground_manipulation", "speaker", "alignment", "prior_manipulation"), sep="/")%>%
  mutate(value = `1`,
         model="prior_only",
         prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))%>%
  select(-`1`)

```

##### Flat prior model 

```{r model flat prior ex4, include = FALSE}
predictions.flat.prior.ex4 <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.predPrior
var noise = dataFromR.noise[0]

var conditionOutput = map(function(conditionInfo){

   var conditionSpecificPriors = [.5, .5, .5] 

   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors)
   var noisyModelPredictions = addNoise(modelPredictions, noise)

  return  extend([conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment+ "/" + conditionInfo.prior_manipulation, Math.exp(noisyModelPredictions.score(1))])

}, allConditions)

conditionOutput

'
```


```{r predictions flat prior model ex 4, include = FALSE}

ex4_flat_prior_model <- webppl(
  program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex4, sep='\n'),
  data = list(allData = adult_ex4_data, allConditions = allConditions, predPrior = predPrior, noise = ex3_flat_prior_model_noise$mean),
  data_var = "dataFromR"
)

# model predictions
ex4_flat_prior_model_pred <- ex4_flat_prior_model %>%
separate(`0`, into = c("common_ground_manipulation", "speaker", "alignment", "prior_manipulation"), sep="/")%>%
  mutate(value = `1`,
         model="flat_prior",
         prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))%>%
  select(-`1`)
```


```{r}
# combine model predictions with data 

# summarize data 
adult_ex4_data_summary <- adult_ex4_data %>%
  mutate(prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))%>%
  mutate(model = "data") %>%
  group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
  summarize(k = sum(correct_inf), n = n())%>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         ci_lower  = qbeta(.025, a, b),
         ci_upper = qbeta(.975, a, b),
         mean = (a-1)/(a+b-2))%>%
  select(-a,-b,-n,-k)

# summarize model predictions
ex_4_model_pred <- bind_rows(
  ex4_pragm_model_pred,
  ex4_prior_only_model_pred,
  ex4_flat_prior_model_pred
) %>%
  group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
  rename(mean = value)%>%
  summarise(mean = mean,
            ci_lower = mean,
            ci_upper= mean)

# combine model predictions and data

ex_4_pred <- bind_rows(
  ex_4_model_pred,
  adult_ex4_data_summary
)

#saveRDS(ex_4_pred, "../../stats/saves/ex4_model_predictions.rds")

```

##### Plot model predictions and data

```{r plot ex4 model predictions and data}
ggplot(data = ex_4_pred, aes(x = alignment, y = mean, col = model)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), size = .4,  position = position_dodge(width = .5), pch = 5)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Choosing More Informative")+
  facet_grid ( prior_manipulation ~ common_ground_manipulation + speaker) +
  theme_few() + 
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_color_manual(name="Model",
                     breaks=c("data","pragmatic","flat_prior","prior_only"),
                     values= c("black","#859900","#6c71c4","#b58900"))+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
```

##### Correlation plot model predictions and data

```{r plot }
## correlation round 1

ex_4_cor_plot <- ex_4_pred %>%
  ungroup()%>%
  filter(model != "data") %>%
  mutate(data_mean = rep(ex_4_pred%>%filter(model == "data")%>%pull(mean),3),
         data_ci_lower = rep(ex_4_pred%>%filter(model == "data")%>%pull(ci_lower),3),
         data_ci_upper = rep(ex_4_pred%>%filter(model == "data")%>%pull(ci_upper),3))
  


ggplot(data = ex_4_cor_plot,aes(x = mean, y = data_mean, col = prior_manipulation)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
  geom_point(size = 2)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .7)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid ( ~ model) +
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = data_mean), inherit.aes = F, size = 3)+
  theme_few(base_size = ) + 
  scale_colour_ptol()
```

### Model comparison

```{r model likelihood rsa ex4, include = FALSE}
loglike.rsa.ex4 <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.predPrior
var noise = dataFromR.noise[0]

var model = function(){

var conditionOutput = map(function(conditionInfo){

  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})

    var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})

    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].prior)
   
    var noisyModelPredictions = addNoise(modelPredictions, noise)

    var loglike = Binomial({
        p: Math.exp(noisyModelPredictions.score(1)), 
        n: conditionSpecificData.length}).score(
      sum(_.map(conditionSpecificData, "correct_inf"))
    )

  return  loglike

  }, allConditions)

  return sum(conditionOutput)

}
'
```

```{r model likelihood prior only ex4 , include = FALSE}
loglike.prior.only.ex4 <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.predPrior
var noise = dataFromR.noise[0]

var model = function(){

var conditionOutput = map(function(conditionInfo){

  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})

   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})

  var modelPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].prior}));
      return obj.shape == "circle" ? 1 : 0
  }})

   var noisyModelPredictions = addNoise(modelPredictions, noise)

    var loglike = Binomial({
        p: Math.exp(noisyModelPredictions.score(1)), 
        n: conditionSpecificData.length}).score(
      sum(_.map(conditionSpecificData, "correct_inf"))
    )

  return  loglike

  }, allConditions)

  return sum(conditionOutput)
}
'
```

```{r model likelihood flat prior ex4, include = FALSE}
loglike.flat.prior.ex4 <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.predPrior
var noise = dataFromR.noise[0]

var model = function(){

var conditionOutput = map(function(conditionInfo){

  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})

   var conditionSpecificPriors = [.5, .5, .5] 

   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors)
   var noisyModelPredictions = addNoise(modelPredictions, noise)

    var loglike = Binomial({
        p: Math.exp(noisyModelPredictions.score(1)), 
        n: conditionSpecificData.length}).score(
      sum(_.map(conditionSpecificData, "correct_inf"))
    )

  return  loglike

  }, allConditions)

  return sum(conditionOutput)
}
'
```

```{r ex 4 model comparison}
# ex4_pragm_model_loglike <- webppl(
#   program_code = paste(rsaUtils, rsaModel, loglike.rsa.ex4, sep='\n'),
#   data = list(allData = adult_ex4_data, allConditions = allConditionsEx4, predPrior = predPriorEx4, noise = ex3_pragm_model_noise$mean),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4, 
#   cores = 4,
#   inference_opts = list(method = "forward", samples = 5000)
# ) %>%
#   saveRDS("../../stats/saves/ex4_pragm_model_loglike.rds")

ex4_pragm_model_loglike <- readRDS("../../stats/saves/ex4_pragm_model_loglike.rds")%>%
  mutate(model = "pragmatic")%>%
  group_by(model)%>%
  summarize(logP = logSumExp(value))

# ex4_prior_only_model_loglike <- webppl(
#   program_code = paste(rsaUtils, rsaModel, loglike.prior.only.ex4, sep='\n'),
#   data = list(allData = adult_ex4_data, allConditions = allConditionsEx4, predPrior = predPriorEx4, noise = ex3_pragm_model_noise$mean),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4, 
#   cores = 4,
#   inference_opts = list(method = "forward", samples = 5000)
# ) %>%
#   saveRDS("../../stats/saves/ex4_prior_only_model_loglike.rds")

ex4_prior_only_model_loglike <- readRDS("../../stats/saves/ex4_prior_only_model_loglike.rds")%>%
  mutate(model = "prior_only")%>%
  group_by(model)%>%
  summarize(logP = logSumExp(value))

# ex4_flat_prior_model_loglike <- webppl(
#   program_code = paste(rsaUtils, rsaModel, loglike.flat.prior.ex4, sep='\n'),
#   data = list(allData = adult_ex4_data, allConditions = allConditionsEx4, predPrior = predPriorEx4, noise = ex3_pragm_model_noise$mean),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4, 
#   cores = 4,
#   inference_opts = list(method = "forward", samples = 5000)
# ) %>%
#   saveRDS("../../stats/saves/ex4_flat_prior_model_loglike.rds")

ex4_flat_prior_model_loglike <- readRDS("../../stats/saves/ex4_flat_prior_model_loglike.rds")%>%
  mutate(model = "flat_prior")%>%
  group_by(model)%>%
  summarize(logP = logSumExp(value))


ex4_model_comparison <- bind_rows(
  ex4_pragm_model_loglike,
  ex4_prior_only_model_loglike,
  ex4_flat_prior_model_loglike
)%>%
  mutate(model = reorder(model,logP))

#saveRDS(ex4_model_comparison, "../../stats/saves/ex4_model_comparison.rds")
```

##### Plot for likelihoods

```{r}
ggplot(ex4_model_comparison, aes(x = model, y = logP, col = model))+
  geom_segment( aes(x=model, xend=model, y=0, yend=logP), col = "black", size = 1)+
  geom_point(size = 7)+
  theme_few()+ 
  xlab("Model")+
  ylab("Log-likelihood")+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(col = F)+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#b58900","#859900","#6c71c4"))
```


##### Bayes factors

```{r}
ex4_bf <- data.frame(
  comparison = c("pragmatic vs. prior_only","pragmatic vs. flat_prior", "flat_rior vs. prior_only"),
  bayes_factor = c(
    exp(ex4_model_comparison$logP[ex4_model_comparison$model== "pragmatic"] - ex4_model_comparison$logP[ex4_model_comparison$model== "prior_only"]),
    exp(ex4_model_comparison$logP[ex4_model_comparison$model== "pragmatic"] - ex4_model_comparison$logP[ex4_model_comparison$model== "flat_prior"]),
    exp(ex4_model_comparison$logP[ex4_model_comparison$model== "flat_prior"] - ex4_model_comparison$logP[ex4_model_comparison$model== "prior_only"]))
)

ex4_bf%>%
  kable(digits = 2)
```
#### Appendix: Model predictions with inferred noise

```{r model rsa noise ex4, include = FALSE}
predictions.rsa.ex4 <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.predPrior

var model = function(){
   var noise = uniformDrift({a: 0, b:1, width: 0.1})

  var conditionOutput = map(function(conditionInfo){

  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})

   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})

   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].prior)
   var noisyModelPredictions = addNoise(modelPredictions, noise)

   map(function(d){ 
      observe(noisyModelPredictions, d.correct_inf)
    }, conditionSpecificData)


  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment+ "/" + conditionInfo.prior_manipulation, Math.exp(noisyModelPredictions.score(1))]

}, allConditions)

  return extend(_.fromPairs(conditionOutput), {noise: noise})

}
'
```

```{r predictions pragmatic model ex 4 inf noise, include = FALSE}

# ex4_pragm_model_inf_noise <- webppl(
#   program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex4, sep='\n'),
#   data = list(allData = adult_ex4_data, allConditions = allConditionsEx4, predPrior = predPriorEx4),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
# ) %>%
#   saveRDS("../../stats/saves/ex4_pragm_model_inf_noise.rds")

ex4_pragm_model_inf_noise <- readRDS("../../stats/saves/ex4_pragm_model_inf_noise.rds")

# model predictions
ex4_pragm_model_pred_inf_noise <- ex4_pragm_model_inf_noise %>%
  filter(!(Parameter %in% c("noise")))  %>%
  separate(Parameter, into = c("common_ground_manipulation", "speaker", "alignment", "prior_manipulation"), sep="/")%>%
  mutate(model="pragmatic",
         prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))


## noise parameter
ex4_pragm_model_noise_inf_noise <- ex4_pragm_model_inf_noise %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

```


```{r model prior only ex4 , include = FALSE}
predictions.prior.only.ex4 <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.predPrior

var model = function(){
   var noise = uniformDrift({a: 0, b:1, width: 0.1})

  var conditionOutput = map(function(conditionInfo){

  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})

   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})

  var modelPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].prior}));
      return obj.shape == "circle" ? 1 : 0
  }})

   var noisyModelPredictions = addNoise(modelPredictions, noise)

   map(function(d){ 
      observe(noisyModelPredictions, d.correct_inf)
    }, conditionSpecificData)


  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment+ "/" + conditionInfo.prior_manipulation, Math.exp(noisyModelPredictions.score(1))]

}, allConditions)

return extend(_.fromPairs(conditionOutput), {noise: noise})

}
'
```

```{r predictions prior only model ex 4 inf noise, include = FALSE}

# ex4_prior_only_model_inf_noise <- webppl(
#   program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex4, sep='\n'),
#   data = list(allData = adult_ex4_data, allConditions = allConditions, predPrior = predPrior),
#   data_var = "dataFromR",
#   model_var = "model",
#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
# ) %>%
#   saveRDS("../../stats/saves/ex4_prior_only_model_inf_noise.rds")

ex4_prior_only_model_inf_noise <- readRDS("../../stats/saves/ex4_prior_only_model_inf_noise.rds")

# model predictions
ex4_prior_only_model_pred_inf_noise <- ex4_prior_only_model_inf_noise %>%
  filter(!(Parameter %in% c("noise")))  %>%
  separate(Parameter, into = c("common_ground_manipulation", "speaker", "alignment", "prior_manipulation"), sep="/")%>%
  mutate(model="prior_only",
         prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))


## noise parameter
ex4_prior_only_model_noise_inf_noise <- ex4_prior_only_model_inf_noise %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

```

```{r model flat prior ex4, include = FALSE}
predictions.flat.prior.ex4 <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.predPrior

var model = function(){
   var noise = uniformDrift({a: 0, b:1, width: 0.1})

  var conditionOutput = map(function(conditionInfo){

  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})

   var conditionSpecificPriors = [.5, .5, .5] 

   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors)
   var noisyModelPredictions = addNoise(modelPredictions, noise)

   map(function(d){ 
      observe(noisyModelPredictions, d.correct_inf)
    }, conditionSpecificData)


  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment+ "/" + conditionInfo.prior_manipulation, Math.exp(noisyModelPredictions.score(1))]

}, allConditions)

  return extend(_.fromPairs(conditionOutput), {noise: noise})

}
'
```


```{r predictions flat prior model ex 4 inf noise, include = FALSE}

# ex4_flat_prior_model_inf_noise <- webppl(
#   program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex4, sep='\n'),
#   data = list(allData = adult_ex4_data, allConditions = allConditions, predPrior = predPrior),
#   data_var = "dataFromR",
#   model_var = "model",
#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
# ) %>%
#   saveRDS("../../stats/saves/ex4_flat_prior_model_inf_noise.rds")

ex4_flat_prior_model_inf_noise <- readRDS("../../stats/saves/ex4_flat_prior_model_inf_noise.rds")

# model predictions
ex4_flat_prior_model_pred_inf_noise <- ex4_flat_prior_model_inf_noise %>%
  filter(!(Parameter %in% c("noise")))  %>%
  separate(Parameter, into = c("common_ground_manipulation", "speaker", "alignment", "prior_manipulation"), sep="/")%>%
  mutate(model="flat_prior",
         prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))


## noise parameter
ex4_flat_prior_model_noise_inf_noise <- ex4_flat_prior_model_inf_noise %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

```


# Children

## RSA model code
```{r rsa model}

childRsaModel <- '
var literalListener = cache(function(utterance, priorProbs){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior); 
var lexicon = lexiconObject[lexiconName];
var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
if ("label" in utterance) {
 var truthValue = lexicon(utterance, obj);
 condition(truthValue)
}
if (utterance.point) {
 var truthValuePoint = point(utterance, obj);
 condition(truthValuePoint)
}
return obj.shape 
}})
})

var speaker = cache(function(obj, lexiconName, priorProbs, speakerOptimality){
Infer({method: "enumerate", model: function(){
var utterance = utterancePrior(obj, lexiconName);
var L0 = literalListener(utterance, priorProbs);
 factor(speakerOptimality * L0.score(obj.shape))
return utterance
}})
})

var pragmaticListener = cache(function(utterance, priorProbs, speakerOptimality){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior);
var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
var S1 = speaker(obj, lexiconName, priorProbs, speakerOptimality);
observe(S1, utterance)
return obj.shape == "circle" ? 1 : 0
}})
})


var addNoise = function(dist, noiseParam){
   Infer({model: function(){ 
      return flip(noiseParam) ? uniformDraw([0, 1]) : sample(dist)
    }
   })
}
'
```

## Model parameters and data

```{r ex3 data}
# children ex3 data
child_ex3_data <-read_csv(file="../../stats/data/child_ex3.csv") 
```

```{r}
# load data from ex1 manipulation experiments to set speaker optimality parameter
child_ex1_data <-read_csv(file="../../stats/data/child_ex1.csv")
# load data from ex2 experiment to set priors
child_ex2_data <-read_csv(file="../../stats/data/child_ex2.csv") 
```

```{r}
childModelParam <- '
var prefData = dataFromR.prefData
var infData = dataFromR.infData

var all_conditions = levels(prefData, "condition")

var model  = function(){

  var so_slope = uniformDrift({a: -2, b: 2, width: 0.4})
  var so_int = uniformDrift({a: -2, b: 2, width: 0.4})

  foreach(function(row){
  
  var age = row.age_num
  var speakerOptimality = so_int  + so_slope * (age - infData[0].minage)
    
    var inf_priorProbs = [.5, .5, .5] 
    
  var rsaPredictions = pragmaticListener({label: "dax", point: 2 },
   inf_priorProbs, speakerOptimality) 
   observe(rsaPredictions, row.correct)

  }, infData)

  
  var pref_params = map(function(cndtn){

    var conditionData = _.filter(prefData, {condition: cndtn})
    
    var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
    var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})    
    
    foreach(function(row){

      var age = row.age_num

      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))
      var priorProbs= [1-priorReg, priorReg]

      var priorPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: prior_objects, ps: priorProbs}));
      return obj.shape == "circle" ? 1 : 0
      }})
      
      observe(priorPredictions, row.correct)

    }, conditionData)
    
    return [
      {param: "pref_int", val: pref_int, condition: cndtn}, 
      {param: "pref_slope", val: pref_slope, condition: cndtn}
    ]
    
  }, all_conditions)
  
        
  return _.flatten(pref_params).concat(
    [
      { param: "so_slope", val: so_slope},
      { param: "so_int", val: so_int}
    ]
  )
}
'
```

```{r}
# child_model_param<- webppl(
#   program_code = paste(rsaUtils, childRsaModel, childModelParam , sep='\n'),
#   data = list(prefData = child_ex2_data, infData = child_ex1_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
# )%>%
#   saveRDS("../../stats/saves/child_model_param.rds")
  

child_model_param <- readRDS("../../stats/saves/child_model_param.rds")%>%
  select(value) %>%
  map_df(bind_rows)%>%
  group_by(param,condition)%>%
  summarise(param_map = estimate_mode(val))%>%
  mutate(cond = paste(param,condition, sep = "_"))%>%
  ungroup()%>%
  select(cond,param_map)%>%
  spread(cond,param_map)%>%
  rename(so_int = so_int_NA,
         so_slope = so_slope_NA)

```

```{r}
# visualize model priors in comparison to data 
child_prior_plot <- child_ex2_data %>%
  group_by(id,age_num,minage,condition)%>%
  summarise(correct = mean(correct))%>%
  mutate(model = ifelse(condition == "different_speaker",
                        plogis(child_model_param$pref_int_different_speaker + child_model_param$pref_slope_different_speaker * (age_num-minage)),
                        plogis(child_model_param$pref_int_same_speaker + child_model_param$pref_slope_same_speaker * (age_num-minage)
                        )))

  
ggplot(data = child_prior_plot, aes(x = age_num, y = correct, col = condition)) +
  geom_jitter(alpha = 0.5, height = 0.02, width = 0)+
  geom_smooth(aes(fill = condition),method = "lm", se = T, alpha = .5, size = .7)+
  geom_line(aes(x = age_num, y = model, col = condition), size = 1.5, lty = 2)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="Age",y="Proportion Correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_color_solarized(name = "Condition")+
  scale_fill_solarized(name = "Condition")
```

```{r}
# visualize speaker optimality in comparison to data 
child_so_plot <- child_ex1_data %>%
  group_by(id,age_num,minage)%>%
  summarise(correct = mean(correct))%>%
  mutate(model = child_model_param$so_int + child_model_param$so_slope * (age_num - minage))

ggplot(data = child_so_plot, aes(x = age_num, y = model)) +
  geom_line(alpha = .5, size = .7)+
  labs(x="Age",y="Speaker optimality parameter")+
  theme_few() +
  geom_hline(yintercept = 0, lty=2)+
  ylim(-3,3)+
  guides(alpha = F)
```

```{r}
ex3_model_data <- child_ex3_data%>%
  mutate(so_int = child_model_param$so_int,
         so_slope = child_model_param$so_slope,
         pref_int_different_speaker = child_model_param$pref_int_different_speaker,
         pref_slope_different_speaker = child_model_param$pref_slope_different_speaker,
         pref_int_same_speaker = child_model_param$pref_int_same_speaker,
         pref_slope_same_speaker = child_model_param$pref_slope_same_speaker,
         so = so_int+so_slope*(age_num-min(age_num)),
         diff_prior = plogis(pref_int_different_speaker+pref_slope_different_speaker*(age_num-min(age_num))),
         same_prior = plogis(pref_int_same_speaker+pref_slope_same_speaker*(age_num-min(age_num))))%>%
  group_by(id,trial)%>%
        mutate(priorProbs = ifelse(speaker == "same_speaker" & alignment == "congruent", list(c(1-same_prior,1-same_prior,same_prior)),
                                   ifelse(speaker == "different_speaker" & alignment == "congruent", list(c(1-diff_prior,1-diff_prior,diff_prior)),
                                          ifelse(speaker == "same_speaker" & alignment == "incongruent", list(c(same_prior,same_prior,1-same_prior)),
                                                 list(c(diff_prior,diff_prior,1-diff_prior))
 
                                   ))))%>%
  ungroup()%>%
  select(speaker,age_num,minage,alignment,so,priorProbs,correct_inf)

```
## Model predictions

### Pragmatic model

```{r}
child.ex3.rsa.predictions <-'

var allData = dataFromR.ex3data

var output = map(function(row){

    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)

    return extend([row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(modelPredictions.score(1))])

}, allData)

output

'
```

```{r}
child_ex3_pragm_model<- webppl(
  program_code = paste(rsaUtils, childRsaModel, child.ex3.rsa.predictions , sep='\n'),
  data =list(ex3data = ex3_model_data),
  data_var = "dataFromR"
)

# model predictions
child_ex3_pragm_model_predictions <- child_ex3_pragm_model %>%
  separate(`0`, into = c("age", "speaker", "alignment"), sep="/")%>%
  mutate(value = `1`,
         model="pragmatic",
         age = as.numeric(age))%>%
  select(-`1`)
```

### Prior only model

```{r}
child.ex3.prior.only.predictions <-'

var allData = dataFromR.ex3data

  var output = map(function(row){

      var modelPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: row.priorProbs}));
      return obj.shape == "circle" ? 1 : 0
       }})

    return  extend([row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(modelPredictions.score(1))])

}, allData)

 output

'
```

```{r}
child_ex3_prior_only_model<- webppl(
  program_code = paste(rsaUtils, childRsaModel, child.ex3.prior.only.predictions , sep='\n'),
  data =list(ex3data = ex3_model_data),
  data_var = "dataFromR"
)

# model predictions
child_ex3_prior_only_model_predictions <- child_ex3_prior_only_model %>%
  separate(`0`, into = c("age", "speaker", "alignment"), sep="/")%>%
  mutate(value = `1`,
         model="prior_only",
         age = as.numeric(age))%>%
  select(-`1`)

```

### Flat prior model

```{r}
child.ex3.flat.prior.predictions <-'

var allData = dataFromR.ex3data

  var output = map(function(row){
    
    var prior = [.5, .5, .5] 

    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, prior,row.so)

    return  extend([row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(modelPredictions.score(1))])

}, allData)

output

'
```

```{r}
child_ex3_flat_prior_model<- webppl(
  program_code = paste(rsaUtils, childRsaModel, child.ex3.flat.prior.predictions , sep='\n'),
  data =list(ex3data = ex3_model_data),
  data_var = "dataFromR")


# model predictions
child_ex3_flat_prior_model_predictions <- child_ex3_flat_prior_model %>%
  separate(`0`, into = c("age", "speaker", "alignment"), sep="/")%>%
  mutate(value = `1`,
         model="flat_prior",
         age = as.numeric(age))%>%
  select(-`1`)

```

### Plot model predictions and data

```{r}
child_model_predictions <- bind_rows(
  child_ex3_pragm_model_predictions,
  child_ex3_flat_prior_model_predictions,
  child_ex3_prior_only_model_predictions
  )

plot_child_ex3_data <- child_ex3_data%>%
  group_by(age_num,speaker,alignment)%>%
  summarise(mean = mean(correct_inf))

ggplot(child_model_predictions)+
  #geom_jitter(data = plot_child_ex3_data, aes(x = age_num, y = mean), width = .025,height = .025, alpha = .2)+
  geom_line(aes(x = age, y = value, col = model), size = 1, alpha = 1, linetype = 1) + 
  geom_smooth(data = child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 1.5,  se = T,  alpha = .5)+
  #geom_hline(yintercept = 0.5, lty=2)+
  labs(y="proportion more informative")+
  ylim(-0.05,1.05)+
  facet_grid(speaker~alignment)+
  theme_few()+
  scale_color_manual(name="Model",
                     breaks=c("pragmatic","flat_prior","prior_only"),
                     values= c("#859900","#6c71c4","#b58900"))+
  scale_fill_manual(name="Model",
                     breaks=c("pragmatic","flat_prior","prior_only"),
                     values= c("#859900","#6c71c4","#b58900"))

```

### Correlation plot model predictions and data

```{r}
child_cor_data <- child_ex3_data %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  group_by(speaker, alignment, age_bin) %>%
  summarize(k = sum(correct_inf), n = n())%>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         Data_ci_lower  = qbeta(.025, a, b),
         Data_ci_upper = qbeta(.975, a, b),
         Data = (a-1)/(a+b-2))%>%
  select(-a,-b,-n,-k)

child_cor_model <- child_model_predictions %>%
  mutate(age = ifelse(age<4,"3","4"))%>%
  group_by(model,speaker,alignment, age)%>%
  summarise(Model = mean(value))
  

child_cor_plot <- child_cor_model %>%
  ungroup()%>%
  mutate(Data = rep(child_cor_data$Data,3),
         Data_ci_lower = rep(child_cor_data$Data_ci_lower,3),
         Data_ci_upper  =rep( child_cor_data$Data_ci_upper,3))


ggplot(data = child_cor_plot,aes(x = Model, y = Data, col = age)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_point(size = 3)+
  geom_errorbar(aes(ymin = Data_ci_lower, ymax = Data_ci_upper),width = 0,size = .5)+
  coord_fixed()+
  facet_grid(~model)+
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = Model, y = Data), inherit.aes = F)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  theme_few() + 
  scale_colour_ptol()
```

